Spfy: an integrated graph-based sequence database for real-time prediction of Escherichia coli phenotypes

### 2018-02-02 paper-webserver.tex
START: cleanup of the comparison section (to BAP/IRIDA) to focus on the data storage

% namely galaxy
Existing scientific workflow technologies such as Galaxy \cite{goecks2010galaxy}, and pipelines such as the Bacterium Analysis Pipeline (BAP) \cite{thomsen2016bacterial} and the Integrated Rapid Infectious Disease Analysis (IRIDA) platform \url{http://www.irida.ca/} help automate the use of WGS data for public-health surveillance.
Galaxy aims to provide a reproducible, computation-based research environment which is accessible to individuals without programming knowledge. Galaxy tackles the problem of linking different analysis software together, by defining interdependencies using a custom schema. A visual workflow editor is also provided for ease of use.
IRIDA is build on top of the Galaxy framework, and adds prebuilt pipelines specific to bioinformatics uses, as well as sequence and result storage. IRIDA takes a project-based approach, with sequences stored per project, and results stored linearly per sequence. IRIDA adds Controls for collaborating on projects, and uses common terms found in the GenEpiO ontology to describe results.

The Bacterial Analysis Platform (BAP), developed out of the Technical University of Denmark, provides an integrated analysis pipeline for bacterial WGS data as a web service.
BAP takes a combined approach to genome analysis including different programs, such as for VF and AMR determination, by default into the pipeline.
A record of the different files generated by an analysis are stored in a relational database, and the record is queried to determine which files are returned to the user \cite{thomsen2016bacterial}.

Like IRIDA and BAP, Spfy automates workflows for users, and like Galaxy, Spfy uses task queues to distribute selected analysis. File uploads begin through the ReactJS-based website, where user-defined analyses options are selected. To these concepts we add Docker containerization for task queue workers, allowing analysis software to safely run in parallel.
% re: Matt "2. When comparing to IRIDA, BAP etc., can mention some differences with Superphy, e.g. the storage of interim result data that allows downstream integrated analysis"
For result storage, existing workflow technologies use relational tables \cite{goecks2010galaxy}, or store resulting files to disk \cite{thomsen2016bacterial}.
Because output from these programs is user-specific or transitory, results from identical comparisons are often recomputed. Additionally, output from different analyses are structured using distinct terminology and formats, which must be converted before they can be compared. Without a unified structure, these conversions quickly become impractical for broad usage. Graph-based storage of all results solves these problems.
% as before
The entire platform is packaged using Docker-Compose, and can be recreated with a simple command. \par

>>>>

% namely galaxy
Existing scientific workflow technologies such as Galaxy \cite{goecks2010galaxy}, and pipelines such as the Integrated Rapid Infectious Disease Analysis (IRIDA) platform \url{http://www.irida.ca/} and the Bacterium Analysis Pipeline (BAP) \cite{thomsen2016bacterial} help automate the use of WGS data for public-health surveillance.
Galaxy aims to provide a reproducible, computation-based research environment which is accessible to individuals without programming knowledge. Galaxy tackles the problem of linking different analysis software together, by defining interdependencies using a custom schema. A visual workflow editor is also provided for ease of use.
IRIDA is build on top of the Galaxy framework, and adds prebuilt pipelines specific to bioinformatics uses, as well as sequence and result storage. IRIDA takes a project-based approach, with sequences stored per project, and results stored linearly per whole-genome sequence. Simiarily, BAP provides an integrated analysis pipeline for bacterial WGS data as a web service.
BAP intergrats different programs, such as for VF and AMR determination, into one pipeline. For result storage, these workflow technologies either use relational tables \cite{goecks2010galaxy}, or store resulting files to disk \cite{thomsen2016bacterial}.

Like IRIDA and BAP, Spfy automates workflows for users, and like Galaxy, Spfy uses task queues to distribute selected analysis.
% re: Matt "2. When comparing to IRIDA, BAP etc., can mention some differences with Superphy, e.g. the storage of interim result data that allows downstream integrated analysis"
Because output from these programs is user-specific or transitory, results from identical comparisons are often recomputed. Additionally, output from different analyses are structured using distinct terminology and formats, which must be converted before they can be compared. Without a unified structure, these conversions quickly become impractical for broad usage. Graph-based storage of all results solves these problems.
